\textbf{Emergency Service Location Optimization in a Multi-Zone County based on Population Distribution}

### 2013-11-22 LaTeX/paper.tex
final

\newpage

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=3.5in]{6point.pdf}
\caption{A graph of the nodes (zones) and edges (travel times).}
\label{satan1}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=3.5in]{greedy6point.pdf}
\caption{A graph of the nodes (zones) with all edges (travel times) greater than 8 removed.}
\label{satan2}
\end{center}
\end{figure}

@@

\newpage
\section{Non-Technical Memo}
To whom it may concern,
After looking at several scenarios, and forming a strategic model, we believe that we have some
suggestions for you regarding how to optimize ambulance placement across zones in your county.

@@

\newpage
\appendix
\section{Code}
The following contains the code for both our brute force location optimizer, as well as the greedy optimizer. Both functions take a parameter $nambulances$, representing the total number of ambulances we have to allocate across the county.

% \inputminted[fontsize=\footnotesize]{python}{../Code/optimizer.py}

>>>>

@@

\newpage
\section{Non-Technical Memo}
To whom it may concern,

After looking at several scenarios, and forming a strategic model, we believe that we have some
suggestions for you regarding how to optimize ambulance placement across zones in your county.

@@

\newpage
\appendix
\section{Code}
The following Python script (optimizer.py) contains the code for both our brute force location optimizer, as well as the greedy optimizer. Both functions take a parameter $nambulances$, representing the total number of ambulances we have to allocate across the county.
\inputminted[fontsize=\footnotesize]{python}{../Code/optimizer.py}

The following file (data.py) contains the data we used for running our optimizer, taken from the provided problem constraints.
\inputminted[fontsize=\footnotesize]{python}{../Code/data.py}
